Facility and Time Step Discretization Effects in Fuel Cycle Simulation

### 2015-09-14 paper.tex
add reference to evaluation and screening report

>>>>

The scenario used is a transition from a the current once-through light water
reactor (LWR) fleet to a full sodium fast reactor (SFR) fuel cycle known as
EG-23 in the Department of Energy's (DOE) Advanced Nuclear Fuel Cycle Options
report \cite{wigeland_nuclear_2014}. Scenario and transition details were
patterned after ongoing work by the DOE in their Fuel Cycle Options campaign.
